\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}

%====================
% EXPERIENCE A
%====================
\subsection{{Senior Software Engineer / TapCheck \hfill Mar 2020 --- Feb 2022}}
\subtext{Emcentrix LLC \hfill Islamabad, Pakistan}
\begin{zitemize}
\item Been a part of highly skillful team of developers to deliver an HR solution.
\item Maintained existing applications and designed and developed new applications.
\item Increased server query response by 10\% using \textbf{{Entity Framework Core}}.

\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{Associate Software Engineer / New Parts System \hfill Feb 2016 --- Mar 2020}}
\subtext{Komatsu Pakistan Soft (pvt) Ltd \hfill Islamabad, Pakistan}
\begin{zitemize}
\item Led a group of 4 developers in the development of \textbf{{C\# .NET}} based software solutions.
\item Maintained existing applications and designed and developed new applications.
\item Debugged and modified software components.

\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection{{Web Developer \& Technical Support Team Lead / Art Gun \hfill Feb 2014 --- Dec 2016}}
\subtext{Telesquad LLC \hfill Rawalpindi, Pakistan}
\begin{zitemize}
\item Monitored and updated back­end data by inter­communicating between \textbf{{.NET}} and \textbf{{MSSQL}}.
\item Built, tested and deployed scale-able, highly available and modular software products.
\item  Led a group of 4 engineers in the Support, and development of \textbf{{C\# .NET}} based software solutions.
\item  Developed object-oriented software using \textbf{{Windows forms}} and \textbf{{ASP.NET}}.
\item  Designed \textbf{{ASP.NET MVC}} based multi­threaded admin web applications.
\item  Developed code fixes and enhancements for inclusion in future code releases and patches.
\item  Collaborated with developers and performance engineers to identify performance bottlenecks.
\item  Debugged and modified software components.
\item  Maintained existing applications and designed and delivered new applications.
\item  Collaborated with product management to build and test systems.
\item  Analyzed and developed relational databases using \textbf{{MSSQL Server 2008/2012}}.
\item  Coded 3 websites using \textbf{{ASP.NET MVC}}.
\item  Modified existing software to correct errors, adapt to new hardware and improve performance.
\item  Wrote and implemented scripts to enhance user experience and integrated scripts with the CRM.

\end{zitemize}

%====================
% EXPERIENCE D
%====================
\subsection{{Web Developer \hfill Aug 2013 --- Feb 2014}}
\subtext{Solosoft Technologies \hfill Abbottabad, Pakistan}
\begin{zitemize}
\item Worked closely with clients to establish problem specifications and system designs.
\item  Performed regression and system level testing to verify software quality and function before it was released.
\item  Developed 12 web applications.
\item  Developed object-oriented software, including CRM.

\end{zitemize}

%====================
% EXPERIENCE E
%====================
\subsection{{Web Developer \hfill Jan 2013 --- Mar 2013}}
\subtext{FeathersSoft technologies \hfill Abbottabad, Pakistan}
\begin{zitemize}
\item Developed 5 web applications.
\item Did Software testing and trouble shooting.

\end{zitemize}

\end{document}